R Notebook

### 2021-06-20 paper-calculations.Rmd
more figures

BAEL data 
```{r}
bael <- read_csv("data/bael.csv") %>%
  na.omit() %>%
  unite(period, year:yearhalf, sep = ".") %>%
  rename(region_name = nazwa_miasta)
```

@@

Figure 4 Number of monthly active users of selected apps in Poland by country, age and gender between 2018 and 2020

@@

Figure 5 -- Point and 95\% interval of ratio of the number of active users and the LFS working 18--65 population by app for 2020HY1. Note that Y axis differs between the apps

@@

Figure 6 -- Average and standard deviation (Std. Dev.) of activity time by app type, app, weekdays and hours

```{r}
selectivv[[4]] %>%
  mutate(apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                             "Bolt Courier", "Takeaway", "Wolt", "Glover")),
         day = factor(day, c("Mondays-Thursdays", "Fridays-Sundays")))  %>%
  ggplot(data = ., aes(x = as.character(period), y = activity_time, color = apps, group = apps)) +
  geom_line() +
  geom_point() + 
  facet_nested(day ~ category +  hour + statistic)  +
  scale_color_brewer(type = "qual", palette = "Dark2", name = "Apps") +  
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1)) +
  labs(x = "Half-year", y = "Average time (in hours)") + 
  scale_y_continuous(breaks = seq(0,7,1))  -> p4

@@

ggsave(plot = p4, file = "figures/fig-sel-half-time-dev.png", width = 9, height = 5)

@@

>>>>

BAEL data

```{r}
bael <- read_csv("data/bael.csv") %>%
  na.omit() %>%
  unite(period, year:yearhalf, sep = ".") %>%
  rename(region_name = nazwa_miasta)
```

@@

Figure 4 -- by region

```{r}
selectivv[[3]] %>%
  count(category, apps, group, period, wt = number_of_users) %>%
  spread(group, n) %>%
  mutate(fua = `Functional area` - Cities, 
         woj = Voivodeship - `Functional area`) %>%
  select(category, apps, period, cities = Cities, fua, woj) %>%
  gather(geo, val, -apps, -period, -category) %>%
  mutate(geo = factor(geo, c("cities", "fua", "woj"),
                      c("Cities", "Functional UAs", "Voivodeships"))) %>%
  group_by(apps, geo) %>%
  mutate(index = val/val[1],
         diff = val-val[1],
         apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                               "Takeaway", "Wolt", "Glover",  "Bolt Courier"))) %>%
  ggplot(data = ., aes(x = as.factor(period), y = diff/1000, group = apps, color = apps)) +
  geom_line() +
  scale_color_brewer(type = "qual", palette = "Dark2") +  
  facet_grid(category ~ geo, scales = "free_y") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  labs(x = "Period (reference=2018.1)", y = "Change in the number of users\n(in thousands)", color = "Apps") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom") ->  p1b

p1b

ggsave(plot = p1b, file = "figures/fig-sel-diff-hy.png", width = 8, height = 5)
```

Figure 5 Number of monthly active users of selected apps in Poland by country, age and gender between 2018 and 2020

@@

Figure 6 -- Point and 95\% interval of ratio of the number of active users and the LFS working 18--65 population by app for 2020HY1. Note that Y axis differs between the apps

@@

Figure 7 -- Average and standard deviation (Std. Dev.) of activity time by app type, app, weekdays and hours

```{r}
selectivv[[4]] %>%
  mutate(apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                             "Bolt Courier", "Takeaway", "Wolt", "Glover")),
         day = factor(day, c("Mondays-Thursdays", "Fridays-Sundays")))  %>%
  ggplot(data = ., aes(x = as.character(period), y = activity_time, color = apps, group = apps)) +
  geom_line() +
  geom_point() + 
  facet_nested(day ~ category +  hour + statistic)  +
  scale_color_brewer(type = "qual", palette = "Dark2", name = "Apps") +  
  theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom") +
  labs(x = "Half-year", y = "Average time (in hours)") + 
  scale_y_continuous(breaks = seq(0,7,1))  -> p4

@@

ggsave(plot = p4, file = "figures/fig-sel-half-time-dev.png", width = 8, height = 5)

@@

Plots by City, Functional UAs, woi

Table with data

```{r}
spat_tab <-data_frame(city = list("Wrocław", 
                       c("Bydgoszcz", "Toruń"),
                       "Łódź",
                       "Lublin",
                       c("Zielona Góra", "Gorzów Wielkopolski"),
                       "Kraków",
                       "Warszawa",
                       "Opole",
                       "Rzeszów",
                       "Białystok",
                       c("Gdańsk", "Gdynia", "Sopot"),
                       "Katowice",
                       "Kielce",
                       "Olsztyn",
                       "Poznań",
                       "Szczecin"),
           lau  = list("Functional area - Wrocław", 
                       c("Functional area - Bydgoszcz", "Functional area - Toruń"),
                       "Functional area - Łódź",
                       "Functional area - Lublin",
                       c("Functional area - Zielona Góra", "Functional area - Gorzów Wielkopolski"),
                       "Functional area - Kraków",
                       "Functional area - Warszawa",
                       "Functional area - Opole",
                       "Functional area - Rzeszów",
                       "Functional area - Białystok",
                       "Functional area - Trójmiasto",
                       c("Functional area - GMZ", "Functional area - GMZ2"),
                       "Functional area - Kielce",
                       "Functional area - Olsztyn",
                       "Functional area - Poznań",
                       "Functional area - Szczecin"),
           woj = list("dolnośląskie", 
                      "kujawsko-pomorskie",
                      "łódzkie",
                      "lubelskie",
                      "lubuskie",
                      "małopolskie",
                      "mazowieckie",
                      "opolskie",
                      "podkarpackie",
                      "podlaskie",
                      "pomorskie",
                      "śląskie",
                      "świętokrzyskie",
                      "warmińsko-mazurskie",
                      "wielkopolskie",
                      "zachodniopomorskie"))
```

For plot: c(1, 3, 4, 6:10,13:16)
```{r}
plot_regions <- c(1, 3, 4, 6:10,13:16)
```

```{r}

for (i in plot_regions) {

city <- spat_tab[i, "city"][[1]][[1]]
lau <- spat_tab[i, "lau"][[1]][[1]]
woj <- spat_tab[i, "woj"][[1]][[1]]

selectivv[[3]] %>%
  filter((group == "Voivodeship" & region_name == woj) |
         (group == "Functional area" & region_name == lau) | 
         (group == "Cities" & region_name == city)) %>%
  mutate(region_name = str_replace(region_name, "Functional area - ", "FUA: "),
         group = factor(group, c("Cities", "Functional area", "Voivodeship"),
                        ordered = T))  %>%
  arrange(apps, period, group) %>%
  group_by(category, apps, period) %>%
  mutate(n = number_of_users - lag(number_of_users),
         n = ifelse(is.na(n), number_of_users, n),
         period = as.character(period),
         apps = factor(apps, c("Uber", "Bolt Driver", "iTaxi", "FREE NOW",
                               "Takeaway", "Wolt", "Glover",  "Bolt Courier"))) %>%
  ungroup() %>%
  mutate(region_name = factor(region_name, unique(region_name), ordered = T)) %>%
  ggplot(data = ., aes(x = period, y = n, group = apps, color = apps)) +
  geom_line() +
  facet_nested(category ~ region_name, scales = "free_y") + 
  scale_color_brewer(type = "qual", palette = "Dark2") +
  labs(x = "Period", y = "Change in the number of users", color = "Apps") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
        legend.position = "bottom") -> p1_annex

ggsave(plot = p1_annex, file = paste0("figures/fig-annex-", i, ".png"), width = 8, height = 5)

}
```
